---
title: "index"
---


```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
load("brfss2013.RData")
```

##1,What is the data source?
The Behavioral Risk Factor Surveillance System (BRFSS) is the nation’s premier system of health-related telephone surveys that collect state data about U.S. residents regarding their health-related risk behaviors, chronic health conditions, and use of preventive services. 

##2,When were the data collected?
The Newest one is 2016, but I only find the Rdata from 2013

##3,How were they collected?
There are 486,303 records for 2016, by telephone survey. The November update includes recoding of responses for a variable (LASTDEN3) in California’s data and a calculated variable (_RFPAP33) set to missing in eight states which did not ask a question (HADHYST2) correctly for eight months.
4What are the units of analysis?
Number of people, and score for mental health and physical health and BMI index
2. Describe each variable you are planning to use.
For continuous variables, provide the mean, standard deviation and a histogram.


```{r cars}
project1 <- c(brfss2013$educa,brfss2013$sex,brfss2013$income2,brfss2013$physhlth,brfss2013$menthlth,brfss2013$X_bmi5,brfss2013$genhlth,brfss2013$smoke100)
summary(brfss2013$physhlth)
hist(brfss2013$physhlth)
summary(brfss2013$menthlth)
hist(brfss2013$menthlth)
summary(brfss2013$X_bmi5)
hist(brfss2013$X_bmi5)
```